Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-03-25 paper/paper.tex
20200325 15:34

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation. (c) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
\end{figure}

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j}) \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

@@

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (S^x S^y + S^y S^z + S^z S^x) \label{eq:EcFM}
\end{equation}
where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\bm{S}| = 1$. $f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\bm{S}| = 1$ are fulfilled. The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.

Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details). Based on these observation, it is reasonable to say that the ground state of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS. In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$. As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.

\subsection{\label{sec:SectionIIIB}Moment direction of the classcial stripe order}
In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d). For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} is
\begin{eqnarray}
    E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
        & & +\: 2 \Gamma (S^y S^z - S^z S^x - S^x S^y) \label{eq:EcStripeX}
\end{eqnarray}
and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
\begin{subequations}
    \label{eq:whole}
    \begin{align}
        & \mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
        & \mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
        & \mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
    \end{align}
\end{subequations}
see Appendix B for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $S^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction. When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.

@@

For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(b)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3. The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)). The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}. In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction. Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.

\section{\label{sec:SectionV}Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively. (c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information. (d) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.}
\end{figure}

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases. $S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

@@

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction. Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.

Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details). Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS. In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$. As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.

\subsection{\label{sec:SectionIIIB}Moment direction of the classcial stripe order}
In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d). For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} is
\begin{eqnarray}
    E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y) \label{eq:EcStripeX}
\end{eqnarray}
and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero
\begin{subequations}
    \label{eq:whole}
    \begin{align}
        & \mathbf{v}_0: \quad v_{0}^{y}=-v_{0}^{z} = \pm1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
        & \mathbf{v}_1: \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
        & \mathbf{v}_2: \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
    \end{align}
\end{subequations}
see Appendix B for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{v}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{v}_1$ direction. When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{v}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$. The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.

@@

For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3. The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)). Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
\end{figure}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for different model parameters. The $A(\bm{k}, \omega)$ is draw along the $M-\Gamma-M$ path in the first BZ. For the 4 $\times$ 6 cluster we use, there are 24 nonequivalent k-points in the first BZ, and 7 k-points on the $M-\Gamma-M$ path, see Fig.~\ref{fig:ModelDefinition}(d)}
\end{figure}

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases, we calculate the SMSF and spin excitation spectrum for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors} and Fig.~\ref{fig:Spectrum}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}. The ground states of the quantum model in these area are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction. Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.

\section{\label{sec:SectionV}Moment Direction-Exact Diagonalization Results}
\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details. (a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively. (c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
\end{figure}
